Supplemental Materials: \\ \emph{Active-contours driven registration method for structure-informed segmentation of diffusion MR images}

### 2015-04-29 Publications/2015-NeuroImage/00-main.tex

\providecommand{\nvec}[1]{\hat{\mathbf{#1}}}
\providecommand{\suppl}[1]{\href{http://dx.doi.org/mydoi}{Supplemental Materials}, #1}
\providecommand{\isores}[2][]{#2\ensuremath{\times}#2\ensuremath{\times}#2%
\ifthenelse{\equal{#1}{}}{}{ [#1]}\xspace}

@@

\title{Active contours-driven registration method for the structure-informed segmentation of diffusion MR images}

>>>>

\providecommand{\nvec}[1]{\hat{\mathbf{#1}}}
\providecommand{\suppl}[1]{\href{http://figshare.com/s/459c26b4ee8211e493b306ec4bbcf141}{Supplemental Materials}, #1}
\providecommand{\isores}[2][]{#2\ensuremath{\times}#2\ensuremath{\times}#2%
\ifthenelse{\equal{#1}{}}{}{ [#1]}\xspace}

@@

\title{Active contours-driven registration method for the structure-informed segmentation of diffusion MR images\tnoteref{t1}}
\tnotetext[t1]{Supplemental materials to this work will be publicly available upon publication with doi:\href{http://figshare.com/s/459c26b4ee8211e493b306ec4bbcf141}{10.6084/m9.figshare.1397502}.
During the review process, the document is available with the private link.}

### 2015-04-29 Publications/2015-NeuroImage/02-abstract.tex

% -*- root: 00-main.tex -*-
We propose a simultaneous segmentation and registration method called \emph{regseg}
  that uses active contours without edges extracted from structural images.
The contours evolve through a free-deformation field of B-Spline functions that
  optimally maps the surfaces onto the data in the target space.
\emph{Regseg} is intended, but not limited, to correct susceptibility-derived distortions
  in echo-planar imaging.
We proof the concept behind \emph{regseg} on four digital phantoms warped with random
  deformations, and conclude that the precision of the segmentation is subvoxel.
We demonstrate \emph{regseg} in the correction task on 16 real diffusion MRI
  datasets from the \acrlong*{hcp}.
The results suggest that \emph{regseg} overperformed an extended competing method.
We compute the geometrical disagreement of the surfaces registered with \emph{regseg} with
  respect to a ground truth, obtaining a 95\% confidence interval of 0.56 - 0.66 (mm)
  for the Hausdorff distance of mesh vertices in images of 1.25mm isotropic resolution.

>>>>

% -*- root: 00-main.tex -*-
Current applications of whole-brain tractography to \acrlong*{dmri} data require highly precise
  delineations of anatomical structures, which are usually projected from anatomical \acrlong*{t1} images
  by registration.
In this study, we propose \regseg{}, which is a simultaneous segmentation and registration method
  that uses active contours without edges extracted from structural images.
The contours evolve through a free-form deformation field supported by the B-spline basis
  to optimally map the contours onto the data in the target space.
We tested the functionality of \regseg{} using four digital phantoms warped with known and
  randomly generated deformations, where subvoxel accuracy was achieved.
We then applied \regseg{} to a registration/segmentation task using 16 real diffusion MRI
  datasets from the \acrlong*{hcp}, which were warped by realistic and nonlinear distortions that are typically
  present in these data.
We computed the misregistration error of the contours estimated by \regseg{} with respect
  to their theoretical location using the ground truth, thereby obtaining a 95\% CI of 0.56--0.66 mm
  distance between corresponding mesh vertices, which was below the 1.25 mm isotropic resolution of the images.
We also compared the performance of our proposed method with a widely used registration tool, which showed 
  that \regseg{} outperformed this method in our settings.
